Age-related changes in plant growth and traits

### 2016-06-07 scripts/Accessory_figs_20160218.Rmd
small changes to accessory costs figures

#Figure 2. Ternary diagram showing seed_costs
```{r}
ternary <- select(SummarySpp[["mean"]],species,seed_size,prepollen_costs,pack_disp_costs,seed_costs)
ternary$seed_costs = ternary$seed_size + ternary$prepollen_costs + ternary$pack_disp_costs

@@

#Figure 2 continued
```{r}
win.metafile("figs2/Accessory_Costs/Figure03_ternary_diagram_seed_costs.wmf", height=5, width=5)
plot

@@

plot(pack_disp_costs~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required provisioning costs per seed (mg/seed)",xlab="",cex=1.5)
#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$pack_disp_costs,SummarySpp[["se"]]$prepollen_costs)
mod <- lm(log10(postpollen_all_per_seed)~log10(seed_size),SummarySpp[["mean"]])
abline(coef(mod)[1],coef(mod)[2])
abline(coef(mod)[1],1,col="red")
axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)
dev.off()
```

@@

#fixed = BOLE, GRBU, PUTU,

#nearly fixed = EPMI, PELA, LEES
check <- subset(SummarySpp[["mean"]],species=="BOLE")
check$seed_size
check$embryo_endo_size
check$seed_costs
check$prepollen_costs
check$pack_disp_costs
check$pack_disp_costs_plus
check$pack_disp_early_costs
check$seed_early_costs

@@

invest_ind <- subset(InvestmentByPart,individual=="PUTU_152")

ind <- subset(SummaryInd, species=="GRBU"&seed_count>0)
check3 <- select(ind,individual,prepollen_costs,seed_early_costs,prepollen_costs,pack_disp_costs,pack_disp_early_costs,propagule_per_seed,seed_costs)

>>>>

#Figure 3. Ternary diagram showing seed_costs
```{r}
ternary <- select(SummarySpp[["mean"]],species,seed_size,prepollen_costs,pack_disp_costs,seed_costs)
ternary$seed_costs = ternary$seed_size + ternary$prepollen_costs + ternary$pack_disp_costs

@@

#Figure 3 continued
```{r}
win.metafile("figs2/Accessory_Costs/Figure03_ternary_diagram_seed_costs.wmf", height=5, width=5)
plot

@@

plot(pack_disp_costs~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required provisioning costs per seed (mg/seed)",xlab="",cex=1.5)
y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$pack_disp_costs,SummarySpp[["se"]]$pack_disp_costs)
mod <- lm(log10(postpollen_all_per_seed)~log10(seed_size),SummarySpp[["mean"]])
abline(coef(mod)[1],coef(mod)[2])
abline(coef(mod)[1],1,col="red")
axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)
dev.off()
```

@@

#fixed = BAER, BOLE, EPMI, GRBU, GRSP, HATE, HEPU, LEES, PEPU, PELA, PHPH, PUTU

#nearly fixed = PILI
check <- subset(SummarySpp[["mean"]],species=="BOLE")
check$seed_size
check$embryo_endo_size
check$seed_costs
check$prepollen_costs
check$pack_disp_costs
check$pack_disp_costs_plus
check$pack_disp_early_costs
check$seed_early_costs

@@

invest_ind <- subset(InvestmentByPart,individual=="GRSP_802" & (part=="inflorescence_stalk"| part=="inflorescence_stalk_in_fruit"))
invest_ind
weight_total <- sum(invest_ind$weight)
weight_total
count2 <- sum(invest_ind$count)

invest_ind2 <- subset(InvestmentByPart,individual=="COER_807")
invest_ind2
count_total <- sum(invest_ind2$count)
count_total

0.7*weight_total/count_total

ind <- subset(SummaryInd, species=="PUTU"&seed_costs>0)
check3 <- select(ind,individual,prepollen_costs,seed_early_costs,prepollen_costs,pack_disp_costs,pack_disp_gross_costs,pack_disp_early_costs,propagule_per_seed,seed_costs,seed_count,propagule_inv)
